%----------------------------------------
% LaTeX Resume
% Author : Ziady Mubaraq
% Source : https://github.com/ziterz/resume-latex/
% License : MIT
%----------------------------------------

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.3in,top=0.3in]{geometry}

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\setlist{topsep=1mm, parsep=1.75mm, itemsep=-0.1em}

\usepackage{tgschola}
\usepackage[T1]{fontenc}

\usepackage{changepage}
\usepackage{fancyhdr}
\usepackage{multicol}

\hyphenpenalty=10000

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

\setlength{\parindent}{0pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%----------------------------------------
% Custom commands
\newcommand{\header}[1]{
	\vspace{4mm}
	{\large \noindent \textbf{#1}}
	\vspace{1mm}
	\hrule
	\vspace{2mm}
}

\newcommand{\shortitem}[4]{
	\begin{adjustwidth}{}{}
		\textbf{#1} \hfill \ifx&#2& \else \textbf{#2} \fi \\
		\textit{#3} \ifx&#4& \else \hfill #4 \fi
	\end{adjustwidth}
	\vspace{1mm}
}

\newcommand{\longitem}[4]{
	\begin{adjustwidth}{}{}
		\textbf{#1} \hfill \ifx&#2& \else \textbf{#2} \fi \\
		\textit{#3} \ifx&#4& \else \hfill #4 \fi
	\end{adjustwidth}
	\vspace{-1mm}
}

\newcommand{\liststart}{\begin{itemize}[leftmargin=*]}
\newcommand{\listend}{\end{itemize}\vspace{1mm}}

%----------------------------------------
% Resume starts here
\begin{document}

	%----------------------------------------
	% Hero
	\begin{flushleft}
		{\LARGE \textbf{Ziady Mubaraq}} \\
		{\large Software Engineer, Educator}

		\vspace{1mm}
		
		14 Dec 1996 $\mid$ Jakarta, Indonesia  $\mid$ \href{https://wa.me/6285186661414}{(+62) 8518 666 1414} $\mid$ \href{mailto:ziady.mubaraq@gmail.com}{ziady.mubaraq@gmail.com} \\
		\href{https://ziterz.dev}{ziterz.dev}  $\mid$ \href{https://github.com/ziterz}{github.com/ziterz} $\mid$ \href{https://linkedin.com/in/ziterz}{linkedin.com/in/ziterz}        
	\end{flushleft}

	\vspace{-3mm}

	%----------------------------------------
	% Objective
	\header{Objective}
		Seeking a position as a Software Engineer specializing in iOS development, aiming to leverage 4+ years of experience in web and mobile development, including both native and hybrid approaches. Having a proven track record of mentoring and leading teams at coding bootcamps, I maintain a strong work ethic and excel at adapting to any situation.
		\vspace{1mm}

	\setlength{\columnsep}{1.5em}

	%----------------------------------------
	% Multi Column
	\begin{multicols}{2}

		%----------------------------------------
		% Related Projects
		\header{Related Projects}
			\longitem{\href{https://ziterz.dev/projects/riot-boardgame}{Riot Board Game}}{Sep - Nov 2023}{iOS Developer, Game Designer}{}
			\liststart
				\item Developed a hybrid board game with a native iOS companion app that integrates physical and digital elements using NFC technology for interactions.
				\item Using Xcode, SwiftUI, CoreNFC, AVKit, MVVM design pattern, Figma, Illustrator, and Photoshop.
			\listend

			\longitem{\href{https://ziterz.dev/projects/mech-kit}{MechKit}}{Jul - Aug 2023}{iOS Developer, AR Designer}{}
			\liststart
				\item Developed an app for iPadOS to assist you in creating your very own personalized mechanical keyboard.
				\item Using Xcode, SwiftUI, UIKit, CoreData, SceneKit, ARKit, RealityKit, and AVFoundation.
			\listend

			\longitem{\href{https://ziterz.dev/projects/the-academy-times}{The Academy Times}}{May 2023}{iOS Developer, AR Designer}{}
			\liststart
				\item Developed a native iOS app that brings your local newspaper to life using the power of ARKit.
				\item Using Xcode, UIKit, SceneKit, ARKit, and AVKit.
			\listend

			\longitem{\href{https://ziterz.dev/projects/hcis-imeco}{HCIS Imeco}}{Sep 2022 - Jan 2023}{Front End Developer}{}
			\liststart
				\item Developed the HCIS (Human Capital Information System) application for a company, including employee data, salaries, attendance, and company requirements.
				\item Using Vue 3, Pinia, Vite, Maps, and TailwindCSS.
			\listend

			\longitem{\href{https://ziterz.dev/projects/speed-online}{Speed Online}}{Feb - Apr 2022}{Mobile Developer}{}
			\liststart
				\item Developed the Speed Online mobile application for ordering tickets for ship crossings in North Kalimantan.
				\item Using Vue 3, Quasar, Vuex, Maps, WhatsApp OTP, and Xendit Payment Gateway.
			\listend

			\longitem{\href{https://ziterz.dev/projects/jastipinaja}{Jastipin Aja}}{Oct - Dec 2020}{Mobile Developer}{}
			\liststart
				\item Developed the Jastipin Aja mobile application for Aldeoz Group to serve users who miss their regional food during the pandemic era, offering same-day delivery.
				\item Using React, React Native, Paper, Firebase, OneSignal, and Midtrans Payment Gateway.
			\listend

			\longitem{\href{https://ziterz.dev/projects/dicicilaja}{Dicicilaja}}{Jan - Dec 2019}{Lead Android Developer}{}
			\liststart
				\item Developed the Dicicilaja mobile app for Adira Finance, including a marketplace, sales app, branch office, business rewards, simulation, order-in, and inbox.
				\item The application is available on the Play Store and has been downloaded by more than 100,000 users.
				\item Using Android Studio, Java, Kotlin, RxJava, Firebase, and OneSignal.
			\listend

		\columnbreak

		%----------------------------------------
		% Professional Experience
		\header{Professional Experience}
			\longitem{Apple Developer Academy}{Mar - Dec 2023}{Internship}{}
			\liststart
				\item Learn coding, design, and professional skills, such as iOS Development, Swift Programming, Apple Frameworks, Design Patterns, Testing and Human Interface Guidelines (HIG) principles, in a world-class developer environment.
				\item Built applications that are available on TestFlight and the App Store.
			\listend

			\longitem{Hacktiv8 Indonesia}{Jun 2021 - Feb 2023}{Lead Full-Stack JavaScript Instructor}{}
			\liststart
				\item Evaluate and observe the learning process/instructors.
				\item Collaborate with the Instructor Lead and the team to train and supervise new high-quality instructors.
				\item Continuously monitor and maintain curriculum progress.
				\item Teach and ensure that the course material is effectively delivered.
			\listend

			\longitem{Hacktiv8 Indonesia}{Jan 2020 - Jun 2021}{Full-Stack JavaScript Instructor}{}
			\liststart
				\item Teaches, guide and communicate with students.
				\item Monitors and assesses students' progress on a regular basis.
				\item Teaching courses such as Vue 3, Pinia, Vite, React, React Native, Redux, TDD, Jest, Microservices, NoSQL, MongoDB, GraphQL, and Docker.
			\listend
		
		%----------------------------------------
		% Recent Certifications
		\header{Recent Certifications}
			\shortitem{\href{https://www.credly.com/badges/3b51cb14-d2eb-4782-8c96-4d9a3cbb2797}{App Development with Swift Certified User by Apple}}{}{Certificate of Completion - Feb 2024}{}
			\shortitem{\href{https://github.com/ziterz/100days-of-swiftui}{100 Days of SwiftUI by Hacking with Swift}}{}{Certificate of Distinction - Jan 2024}{}
			\shortitem{\href{https://github.com/ziterz/100days-of-swift}{100 Days of Swift by Hacking with Swift}}{}{Certificate of Distinction - Jan 2024}{}
			\shortitem{Apple Developer Academy Certificate}{}{Certificate of Completion - Dec 2023}{}
			\shortitem{\href{https://www.wwdcscholars.com/s/0D25000C-A584-4C3D-A95B-AF574079E4D8/2023}{Swift Student Challenge WWDC23 by Apple}}{}{Swift Student Challenge Winner - May 2023}{}

		%----------------------------------------
		% Educational Background
		\header{Educational Background}
			\shortitem{Apple Developer Academy}{Dec 2023}{iOS Developer}{}
			\shortitem{Indonesia University of Education}{Oct 2019}{Bachelor of Education in Computer Science}{GPA: 3.72}

	\end{multicols}

\end{document}